Do we need detailed demographic data to forecast plant population responses to climate change?

### 2015-03-06 manuscript/suppMat.Rmd
updated for lag ppt

```{r figure_S1, dependson="plot-options", fig.cap="Posterior means (vertical ticks), 75% credible intervals (heavy lines), and 95% credible intervals (light lines) of climate effects on growth at both levels of inferences. The dashed vertical line is at 0, indicating no effect.", fig.width=8, fig.height=7, cache=FALSE, results='hide'}
qbm_quants <- read.csv("../montana/quadBM/vitalRateRegressions/truncNormModel/growthQuants.csv")
qbm_quants <- qbm_quants[137:156,]
qbm_quants <- qbm_quants[-c(9:12),]
coefNames <- c("ppt1", "ppt2", "temp1", "temp2")
qbm_quants$X <- rep(coefNames, each=4)
gQ <- ggplot(qbm_quants, aes(x=species, y=X50., group=species), color="grey25")+
  geom_hline(aes(yintercept=0), linetype="dashed")+
  geom_errorbar(aes(ymin=X2.5., ymax=X97.5.), width=0, position=position_dodge(width=0.5))+
  geom_errorbar(aes(ymin=X25., ymax=X75.), width=0, size=1.25, position=position_dodge(width=0.5))+
  geom_point(size=4, position=position_dodge(width=0.5), shape="|")+
  ylab("Standardized Coefficient Value")+
  xlab("Species")+
  facet_grid(X~.)+
  coord_flip()+
  theme_bw()+
  guides(color=guide_legend(title=""))+
  theme(legend.position="top")+
  ggtitle("Quadrat level")

>>>>

```{r figure_S1, dependson="plot-options", fig.cap="Posterior means (vertical ticks), 75% credible intervals (heavy lines), and 95% credible intervals (light lines) of climate effects on growth at both levels of inferences. The dashed vertical line is at 0, indicating no effect.", fig.width=8, fig.height=7, cache=FALSE, results='hide'}
qbm_quants <- read.csv("../montana/quadBM/vitalRateRegressions/truncNormModel/growthQuants_withLagPpt.csv")
qbm_quants <- qbm_quants[137:160,]
qbm_quants <- qbm_quants[-c(13:16),]
coefNames <- c("ppt1", "ppt2", "lagppt", "temp1", "temp2")
qbm_quants$X <- rep(coefNames, each=4)
gQ <- ggplot(qbm_quants, aes(x=species, y=X50., group=species), color="grey25")+
  geom_hline(aes(yintercept=0), linetype="dashed")+
  geom_errorbar(aes(ymin=X2.5., ymax=X97.5.), width=0, position=position_dodge(width=0.5))+
  geom_errorbar(aes(ymin=X25., ymax=X75.), width=0, size=1.25, position=position_dodge(width=0.5))+
  geom_point(size=4, position=position_dodge(width=0.5), shape="|")+
  ylab("Standardized Coefficient Value")+
  xlab("Species")+
  facet_grid(X~.)+
  coord_flip()+
  theme_bw()+
  guides(color=guide_legend(title=""))+
  theme(legend.position="top")+
  ggtitle("Quadrat level")
